InferentialStats

### 2018-08-30 E2/analysis/exclusions.Rmd
cool

Merge operation lost it  targetSP==NA in data? That's the rows reporting stream on opposite side. Eventually, use those to evaluate swaps. I don't know what happened to it, because it's created in 
exclusions.Rmd, which on line 67 creates the thing merged with estimates that is saved. 
```{r, echo=FALSE}
table(dat$targetSP,useNA="ifany")

>>>>

Merge operation lost   targetSP==NA in data, but now fixed
```{r, echo=FALSE}
table(dat$targetSP,useNA="ifany")

### 2018-08-30 E2/analysis/inferentialStats.Rmd
about to remove loss of one-target opposite stream
cool

Why is there no targetSP==NA in data? That's the rows reporting stream on opposite side. Eventually, use those to evaluate swaps. I don't know what happened to it, because it's created in 
exclusions.Rmd, which on line 67 creates the thing merged with estimates that is saved. 
filter( !is.na(targetSP) )

@@

```{r, echo=FALSE, message=FALSE}
require(ggplot2)
gg<-ggplot(estimates %>% filter(targetSide=="Both"), 
           aes(x=stream, y=efficacy, color=orientation)) + geom_point() + stat_summary(fun.y="mean",geom="point",size=8, alpha=.5) + theme_apa() +ggtitle('nobody excluded')
show(gg)

hh<-ggplot(estimates %>% filter(targetSide=="Both", exclude==FALSE), aes(x=stream, y=efficacy, color=orientation)) + 
  geom_point(position = position_dodge(width = 0.3)) + stat_summary(fun.y="mean",geom="point",size=4, alpha=.5, position = position_dodge(width = 0.3)) + 
  theme_apa() +ggtitle('after exclusions') + 
  stat_summary(fun.data = mean_cl_boot, geom="errorbar", width=0.4, position = position_dodge(width = 0.3))

@@

hh<-ggplot(estimates %>% filter(targetSide=="Both", exclude==FALSE), aes(x=stream, y=latency, color=orientation)) + 
  geom_point(position = position_dodge(width = 0.3)) +  stat_summary(fun.y="mean",geom="point",size=4, alpha=.5, position = position_dodge(width = 0.3)) + 
  theme_apa() +ggtitle('after exclusions') + 
  stat_summary(fun.data =mean_cl_boot, geom="errorbar", width=0.4, position = position_dodge(width = 0.3))
show(hh)

ii<-ggplot(estimates %>% filter(targetSide=="Both", exclude==FALSE), aes(x=stream, y=precision, color=orientation)) + 
  geom_point(position = position_dodge(width = 0.3)) +  stat_summary(fun.y="mean",geom="point",size=4, alpha=.5, position = position_dodge(width = 0.3)) + 
  theme_apa() +ggtitle('after exclusions') + 
  stat_summary(fun.data =mean_cl_boot, geom="errorbar", width=0.4, position = position_dodge(width = 0.3))
show(ii)

@@

Calculate and plot bias. 
```{r , fig.height=20, fig.width=5}
all$leftBias<- all$Left - all$Right
hh<-ggplot(all %>% filter(targetSide=="Both"), 
           aes(x=orientation, y=leftBias)) + facet_grid(dv~., scales="free") +
    stat_summary(fun.y="mean",geom="point",size=4, alpha=.5) + geom_point() +
  stat_summary(fun.data = mean_cl_boot, geom="errorbar", width=0.2) + theme_apa() +

>>>>

@@

```{r, echo=FALSE, message=FALSE}
require(ggplot2)
gg<-ggplot(estimates %>% filter(targetSide=="both"), 
           aes(x=stream, y=efficacy, color=orientation)) + geom_point() + stat_summary(fun.y="mean",geom="point",size=8, alpha=.5) + theme_apa() +ggtitle('nobody excluded')
show(gg)

hh<-ggplot(estimates %>% filter(targetSide=="both", exclude==FALSE), aes(x=stream, y=efficacy, color=orientation)) + 
  geom_point(position = position_dodge(width = 0.3)) + stat_summary(fun.y="mean",geom="point",size=4, alpha=.5, position = position_dodge(width = 0.3)) + 
  theme_apa() +ggtitle('after exclusions') + 
  stat_summary(fun.data = mean_cl_boot, geom="errorbar", width=0.4, position = position_dodge(width = 0.3))

@@

hh<-ggplot(estimates %>% filter(targetSide=="both", exclude==FALSE), aes(x=stream, y=latency, color=orientation)) + 
  geom_point(position = position_dodge(width = 0.3)) +  stat_summary(fun.y="mean",geom="point",size=4, alpha=.5, position = position_dodge(width = 0.3)) + 
  theme_apa() +ggtitle('after exclusions') + 
  stat_summary(fun.data =mean_cl_boot, geom="errorbar", width=0.4, position = position_dodge(width = 0.3))
show(hh)

ii<-ggplot(estimates %>% filter(targetSide=="both", exclude==FALSE), aes(x=stream, y=precision, color=orientation)) + 
  geom_point(position = position_dodge(width = 0.3)) +  stat_summary(fun.y="mean",geom="point",size=4, alpha=.5, position = position_dodge(width = 0.3)) + 
  theme_apa() +ggtitle('after exclusions') + 
  stat_summary(fun.data =mean_cl_boot, geom="errorbar", width=0.4, position = position_dodge(width = 0.3))
show(ii)

@@

Calculate and plot bias. 
```{r , fig.height=20, fig.width=5}
all$leftBias<- all$Left - all$Right
hh<-ggplot(all %>% filter(targetSide=="both"), 
           aes(x=orientation, y=leftBias)) + facet_grid(dv~., scales="free") +
    stat_summary(fun.y="mean",geom="point",size=4, alpha=.5) + geom_point() +
  stat_summary(fun.data = mean_cl_boot, geom="errorbar", width=0.2) + theme_apa() +
